Approximation as Differentiation: Notes

### 2025-05-25 main/introduction.tex
spivak65.

Data provenance aims to answer questions like ``Where did these data come from?'', ``Why are these data in the output?'' and ``How were these data computed?''. Provenance tracking has a wide range of applications, from debugging and program comprehension to improving reproducibility and transparency in scientific workflows. In order to audit any computational process, we need robust and well-founded notions of provenance to track how data are used, how data are computed, and what data influenced a particular outcome. \emph{Program slicing}, first proposed by~\citet{weiser81}, is a collection of techniques for provenance tracking that attempts to take a run of a program and areas of interest in the output, and turn them into the subset of the input and the program that were responsible for generating those specific outputs.

>>>>

To audit any computational process, we need robust and well-founded notions of \emph{provenance} to track how data are used. This allows us to answer questions like ``Where did these data come from?'', ``Why are these data in the output?'' and ``How were these data computed?''. Provenance tracking has a wide range of applications, from debugging and program comprehension \todo{cite1} to improving reproducibility and transparency in scientific workflows \todo{cite2}. \emph{Program slicing}, first proposed by~\citet{weiser81}, is a collection of techniques for provenance tracking that attempts to take a run of a program and areas of interest in the output, and turn them into the subset of the input and the program that were responsible for generating those specific outputs.
